---
title: "index"
author: "Charles Hendrickson"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Welcome

```{r}
# get libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  bbest/clockify,
  dplyr, DT, ggplot2,
  quiet = TRUE)

# CHANGE THESE VARIABLES!
api_txt <- "~/Documents/eds211/clockify_api-key"
project_name <- "crcm-science"

# use API key to authenticate
CLOCKIFY_API_KEY <- readLines(api_txt)
set_api_key(CLOCKIFY_API_KEY)

# get data
d_times <- time_entries_all()
# table(d_times$project_name) # confirm project_name
d_times <- d_times %>%
  filter(
    project_name == !!project_name) %>%
  select(
    task_name, time_start, duration_hrs, 
    user_name, description) %>% 
  arrange(task_name, time_start)
```


Overall our project is over budget because we finished our tasks faster than the number of hours we estimated it would take. 

The burndown for our Literature Review task starts off with 10 hours and only uses up 1 hour total. Thus, this task took less time than originally estimated.
```{r}
time_lit_review <- d_times %>% 
  filter(task_name == 'Literature Review') %>% 
  summarise(sum(duration_hrs))

time_lit_review
```

The burndown for the Data Acquisition task starts off with 10 hours, but we only spent 7.166667 hours on it. Thus, this task took less time than originally estimated 3.84 hours over budget.

```{r}
time_Data_Acquisition <- d_times %>% 
  filter(task_name == 'Data Acquisition') %>% 
  summarise(sum(duration_hrs))

time_Data_Acquisition
```

The burndown for the Model Task starts off with 10 hours, which was under budget becuase it took 11 hours before it gets burned, so the task was not on target with budget.

```{r}
time_model <- d_times %>% 
  filter(task_name == 'Model') %>% 
  summarise(sum(duration_hrs))

time_model
```

The burndown for the Communicate Task starts off with 10 hours, which was under budget becuase it took 1.166667 hours to get it done, so the task was on target with budget.

```{r}
time_communicate <- d_times %>% 
  filter(task_name == 'Communicate') %>% 
  summarise(sum(duration_hrs))

time_communicate
```

## crcm-science {.tabset}


### Overall

```{r}
# plot ALL
plot_burndown(
  d_times,
  beg = as.Date("2021-10-02"), # day before
  end = as.Date("2021-11-21"), # day after
  hrs = 20)

# table ALL
datatable(d_times)
```

### 1. Literature Review

```{r}
task <- "Literature Review"
d_task <- d_times %>% 
  filter(task_name == !!task)
plot_burndown(
  d_task,
  beg = as.Date("2021-10-31"), # day before
  end = as.Date("2021-11-02"), # day after
  hrs = 10)

datatable(d_task)
```

### 2. Data Acquisition

```{r}
task <- "Data Acquisition"
d_task <- d_times %>% 
  filter(task_name == !!task)
plot_burndown(
  d_task,
  beg = as.Date("2021-11-01"), # day before
  end = as.Date("2021-11-05"), # day after
  hrs = 10)

datatable(d_task)

```

### 3. Model 

```{r}
task <- "Model"
d_task <- d_times %>% 
  filter(task_name == !!task)
plot_burndown(
  d_task,
  beg = as.Date("2021-10-01"), # day before
  end = as.Date("2021-10-31"), # day after
  hrs = 10)

datatable(d_task)
```



### 4. Communicate 

```{r}
task <- "Communicate"
d_task <- d_times %>% 
  filter(task_name == !!task)
plot_burndown(
  d_task,
  beg = as.Date("2021-11-01"), # day before
  end = as.Date("2021-11-03"), # day after
  hrs = 10)

datatable(d_task)
```

```{r}
# table ALL
datatable(d_times)
```
